Technical debt is a metaphor in which the consequences of decisions that affect the maintenance of a software system, such as decisions regarding architecture and development practices, are described with attributes of financial debt~\cite{Cunningham:1992}. Economic models proposed by the \TD community quantify debt using the concepts of principal and interest, where principal is the cost to repay the debt incurred by not completing a change and interest is the cost accumulated while the principal is not repaid by completing the change.

Several approaches for estimating principal are based on heuristics that use measures of structural code quality as inputs to models that estimate effort. For example, Nugroho et al.~\cite{Nugroho_etal:2011} provide a model for estimating principal using maintainability ratings based on measures obtained via static analysis of code, and a model for estimating interest using estimates of maintenance effort based on change history of code. Curtis \etal~\cite{Curtis_etal:2012} also provide a model for estimating principal using measures based on static analysis of code, and in their model, principal is a function of the number of problems, the time/effort required to fix each problem, and the cost of fixing a problem.  

Although such models provide the means to estimate debt, it may be difficult to justify reducing technical debt without detailed information about the impact of the debt on developer's day-to-day maintenance activities. Until the debt reaches a point at which it has a substantial impact on the progress or cost of maintenance, developers may be forced to work around areas of the code in which the debt is manifest~\cite{Ozkaya_etal:2011}. Because most developer effort during software maintenance is spent on program comprehension activities such as reading and navigating code~\cite{Fjeldstad_Hamlen:1982,Standish:1984,vonMayrhauser_etal:1997,Ko_etal:2006,LaToza_etal:2006,Tiarks:2011}, understanding the impact of structural-quality-related debt on code comprehension is of critical importance. In this paper, we propose a framework to support continuous estimation of interest payments on technical debt by monitoring the effort that developers must expend to comprehend code as they complete change tasks. 

The framework proposed combines effort data from monitoring developer actions to derive the interest payment with statically measured code maintainability measures to derive the principal.  \Fix{A picture would be good here} The framework calculates comprehension effort with a monitoring tool that records developer actions in the Integrated Development Environment (IDE).  The monitoring tool, named Blaze described in \cite{Snipes2014Experiences}, allows measurements of code navigation actions, class relationships, and edit actions in a temporally sequenced log.  Analyzing this data for each software element provides a measured amount effort the developer expends comprehending the code element in order to perform maintenance actions. With the effort data on code elements, the framework provides a correlation with a structural code measurement indicative of \TD.  This gives continuous estimates for and evidence of how much the \TD drives developer code comprehension effort.

%\Fix{Developers spend more time reading and navigating source code than writing it~\cite{Ko_etal:2006,LaToza_etal:2006}.}
%
%\Fix{Software maintenance accounts for up to 70\% of software development cost~\cite{Boehm:1981}.}
%
%\Fix{Most (about 50\% to 80\%) of developer effort during software maintenance is spent on program comprehension activities~\cite{Fjeldstad_Hamlen:1982,Standish:1984,vonMayrhauser_etal:1997,Tiarks:2011}.}
